Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-25 products/manuscript/Manuscript.qmd
Update2

## Keywords:
**Malaria, Adverse birth outcomes, Gravidity/Parity, Intermittent preventive treatment in pregnancy (IPTp), Sulfadoxine–pyrimethamine, Dihydroartemisinin–piperaquine**

>>>>

**Keywords:**

**Malaria, Adverse birth outcomes, Gravidity/Parity, Intermittent preventive treatment in pregnancy (IPTp), Sulfadoxine–pyrimethamine, Dihydroartemisinin–piperaquine**
